babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-08 article.tex
Numbered lines, arrows look funny

\title{babette: BEAUti, BEAST and Tracer for R}
\author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}

\usepackage{listings}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{pgf}
\usetikzlibrary{arrows,automata}

@@

% Adds numbered lines, thanks to Raphael Scherrer
% \usepackage[switch]{lineno}

@@

sum_stats <- calc_sum_stats(
  out$estimates$birthRate, 
  sample_interval = 1000, burn_in_fraction = 0.1
)

>>>>

\title{babette: BEAUti 2, BEAST2 and Tracer for R}
\author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}

\usepackage{listings}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{pgf}
\usepackage{bm}
\usetikzlibrary{arrows,automata}

@@

% Adds numbered lines
\usepackage{lineno}
\linenumbers

@@

\begin{lstlisting}[language=R, caption=Calculate all summary statistics, label=lst:calc_sum_stats, floatplacement=H]
sum_stats <- calc_sum_stats(
  out$estimates$birthRate, 
  sample_interval = 1000, burn_in_fraction = 0.1
)
\end{lstlisting}
